The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2019-03-14 paper/ms.tex
final?

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}. It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaaguirre2015,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. \kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{triana15,vanreeth18}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence. 
\newpage

@@

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax.  We also calculate \gaia-like stellar bolometric radii using \texttt{isoclassify} \citep{huber2017} using our new spectroscopic \teff measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes spectroscopic \logg, $Z$, and SIMBAD $V$. While not all of our targets have \gaia radii, we find that while there is overall agreement to within a few $\sigma$, the results from stellar modelling are consistently slightly larger than those from \gaia. This discrepancy goes away for most stars when we use our own \texttt{isoclassify} radii, suggesting that this is an effect of \teff calibration. Two stars are noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling. It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax. Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling, but of our sample it has the lowest \gaia parallax over error at only 18.0, and this anomalously high value is likely noise. Agreement for large-radius ($>30 \rsun$) stars is poorer, even though the \gaia parallax-over-error is apparently adequate. This disagreement, unlike for medium radius stars, is pronounced mainly for the \texttt{isoclassify} radii rather than \gaia~DR2, suggesting that our $V$ band bolometric corrections for these more yellow (\gaia $Bp-Rp \sim 0.25$) stars are insufficiently accurate.

@@

\caption{\label{gaia_comparison}
A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue and from our own calculations based on \gaia parallaxes and TRES spectroscopy. There is overall good agreement except for very large radii, except for BD+39~3577 (marked), which we do not understand.}
\end{figure}

>>>>

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}. It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaaguirre2015,2016MNRAS.456.2183D,2018MNRAS.479.4786V}. \kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{triana15,vanreeth18}. %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence. 
% \newpage

@@

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax.  We also calculate \gaia-like stellar bolometric radii using \texttt{isoclassify} \citep{huber2017} using our new spectroscopic \teff measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes spectroscopic \logg, $Z$, and SIMBAD $V$. While not all of our targets have \gaia radii, we find that while there is overall agreement to within a few $\sigma$, the results from stellar modelling are consistently slightly larger than those from \gaia. This discrepancy goes away for most stars when we use our own \texttt{isoclassify} radii, suggesting that this is an effect of \teff calibration. Two stars are noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling. It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax. Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling, but of our sample it has the lowest \gaia parallax over error at only 18.0, and this anomalously high value is likely due to noise. Agreement for large-radius ($>30 \rsun$) stars is somewhat poorer, even though the \gaia parallax-over-error is apparently adequate. This dispersion, unlike for medium radius stars, is more pronounced for the \texttt{isoclassify} radii than for \gaia~DR2, suggesting that our $V$ band bolometric corrections for these more yellow (\gaia $Bp-Rp \sim 0.25$) stars are insufficiently accurate.

@@

\caption{\label{gaia_comparison}
A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue and from our own calculations based on \gaia parallaxes and TRES spectroscopy. There is overall good agreement except for very large radii, and except for BD+39~3577 (marked), which we do not understand.}
\end{figure}
